Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-18 manuscript/manuscript.Rmd
Added gender, other organizations, and religion.
Fixing formatting but now having trouble displaying some of the plots (travel, following news).

@@

- First set of questions (hypotheses) can be answered using the results of the intercept-only model.

@@

- Second set of questions (confirmatory) can be answered using the following upper-level models:
  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
![](output/figures/public-affairs.png)

@@

![](output/figures/social-views.png)

    - Can't get a plot of Religiosity to work.

@@

![](output/figures/charity-and-volunteerism.png)

@@

  ![](output/figures/demographics.png)
    - Gender

    - Marital Status
  ![](output/figures/marital-status.png)

  - Education
  ![](output/figures/education.png)
    - Income
  ![](output/figures/income.png)
    - Race 
    ![](output/figures/race.png)
    - Age 
  ![](output/figures/age.png)

@@

- Third set of questions (exploratory) can be answered using a market simulator.

>>>>

A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.

@@

### First Set of Questions
The first set of questions (hypotheses) can be answered using the results of the intercept-only model.

@@

### Second Set of Questions
The second set of questions (confirmatory) can be answered using the following upper-level models:
  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
    ![](output/figures/public-affairs.png)

@@

![](output/figures/social-views.png)
      - Religiosity
  ![](output/figures/religion.png)

@@

![](output/figures/charity-and-voluntarism.png)  
      - Association membership
  ![](output/figures/other-organizations.png)

@@

  ![](output/figures/demographics.png)
      - Gender
  ![](output/figures/gender.png)  
      - Marital Status
  ![](output/figures/marital-status.png)  
      - Education
  ![](output/figures/education.png)
      - Income
  ![](output/figures/income.png)
      - Race 
    ![](output/figures/race.png)
      - Age 
  ![](output/figures/age.png)

@@

### Third Set of Questions
The third set of questions (exploratory) can be answered using a market simulator.
